%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Feng Yun} % Your name
\address{E-mail: YunFengHIT@outlook.com} % Your address
\address{Github link: \href{https://github.com/Mark-Fenng}{https://github.com/Mark-Fenng}} % Your secondary addess (optional)
% \address{(+country code) phone number\\ emailhere@email.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Harbin Institute of Technology, China} \hfill {\em September 2016 - Present} 
    \begin{itemize}[itemsep=-0.3em]
        \item Bachelor of Engineering(Expected 2020) in Computer Science and Technology\hfill { GPA: 83/100 }
        \item Courses: Advanced C Language and Programming(97/100),Python Programming(98/100),Java Network Programming(91/100),Computer Networks(90/100),Computer System(87/100) etc.
    \end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf  \href{https://github.com/EdgeTranslate/EdgeTranslate}{Edge Translate}}{ - A Browser Extension} \hfill {\em July 2018 - Present}
\begin{itemize}[itemsep=-0.3em]
    \item Designed and developed a browser extension called “Edge Translate” to help users to have better experience on foreign language website reading.
    \item Edge Translate integrates the Google Translate API within the webpage and one simple template render engine is used to dynamically update the page according to translation contents.
    \item Published on the \href{https://chrome.google.com/webstore/detail/edgetranslate/bocbaocobfecmglnmeaeppambideimao}{Chrome} / \href{https://addons.mozilla.org/zh-CN/firefox/addon/edge_translate/}{Firefox} / \href{https://appcenter.browser.qq.com/search/detail?key=edgetranslate&id=bocbaocobfecmglnmeaeppambideimao%20&title=edgetranslate}{QQ browser} web stores and gained over 20,000 weekly active users and received a score of 4.7/5.0.
    \item https://chrome.google.com/webstore/detail/edgetranslate/bocbaocobfecmglnmeaeppambideimao
\end{itemize}

{\bf \href{https://github.com/Mark-Fenng/QingXueFrontEnd}{Qingxue} Website for an Education Company} \hfill {\em December 2017 - April 2018}
\begin{itemize}[itemsep=-0.3em]
    \item Designed and built an education website to provide services including publishing, managing, reserving and purchasing courses.
    \item Front-end pages are implemented with VUE framework and NPM.
    \item Developed a database which included over 30 tables obeying 3NF.
    \item Deployed the system on Ali Cloud using uWSGI as the application server and Nginx server as a reverse proxy, static resource loading and load balancer.
\end{itemize}

{\bf An AI Meme Creation Tool Kit} \hfill {\em January 2019 - June 2019}
\begin{itemize}[itemsep=-0.3em]
    \item Designed and developed a Wechat meme creation tool kit with AI image processing technology to help users to produce memes conveniently instead of using Photoshop.
    \item Applied AI technology for text detection(Connectionist Text Proposal Network), image completion(Statistics of Patch Offsets), character recognition(CRNN) and image retrieval(VGG16).
    \item Participated in Wechat Mini Program Application Development Competition and achieved the National Third Prize.
\end{itemize}
    
{\bf \href{https://github.com/Mark-Fenng/TV-Ratings}{TV Viewing Ratings Analysis}} \hfill {\em November 2018 - January 2019}
\begin{itemize}[itemsep=-0.3em]
    \item Employed Spark to analyze a 10 GB dataset of TV viewing ratings for a local TV station to predict the viewing ratings for the new TV shows.
    \item Cleaned the data with Spark SQL and made a series of statistical tests.
    \item Applied random forest algorithm to predict viewing ratings and applied a user-based collaborative filtering algorithm to recommend TV shows for TV viewers. 
\end{itemize}
\end{rSection}
%--------------------------------------------------------------------------------
%    INTERNSHIP SECTION
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Internship}
    {\bf Luliang Cloud Computing Operation Company} \hfill {\em July 2019 - August 2019}\\
    {Technical engineer assistant}
        \begin{itemize}[itemsep=-0.3em]
            \item Participated in the strategy design and execution phase of several domestic surveying and mapping projects. 
            \item Proposed some optimization ideas to improve the system performance.
        \end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards and Scholarships} 
    \begin{itemize}[leftmargin=0pt,itemsep=-0.3em]
        \item { 2019 Chinese University Computer Competition – WeChat Mini Program Application Development Competition, National Third Prize} \hfill{\em July 2019}
        \item { National College Students Mathematical Modeling Competition, Provincial First Prize} \hfill{\em December 2018}
        \item { Northeastern Three Provinces Mathematical Modeling League, First Prize}  \hfill {\em June 2018}
        \item { Lan Qiao Cup Java Software Development Contest, Provincial Second Prize}  \hfill {\em March 2019}
        \item { Lan Qiao Cup C++ Software Development Contest, Provincial Third Prize}  \hfill {\em April 2018}
    \end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
    \begin{itemize}[leftmargin=0pt,itemsep=-0.3em] 
        \item {\bf Software programming: }
        Java, Javascript,  C, Python, C\#,  Matlab.
        \item {\bf Hardware programming: }
        Verilog, VHDL.
        \item {\bf Big data computing framework: }
        Hadoop, Spark, Pregel.
        \item {\bf Others: }
        Web front-end design and development (NPM, VUE), back-end development (Spring boot, Django) and server deployment, proficient in Linux operation system and mathematical modeling.
    \end{itemize}
\end{rSection}
\end{document}----------------------------

